Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-29 stp/paper_aaai/main.tex
Change result charts, add missing ref, reply comments

%  \pdfinfo{
%/Title (2018 Formatting Instructions for Authors Using LaTeX)
%/Author (AAAI Press Staff)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{}
\maketitle
\begin{abstract}
The problem of integrating heterogeneous data sources in an ontology is of high 
relevance in the database field. Several techniques exist to approach this 
problem. Nonetheless, side constraints on the data integration cannot be easily 
integrated with these tools and thus the results may be inconsistent. We 
present a new approach that combines Machine Learning and 
Constraint Programming techniques, by modelling the data integration problem as 
a Steiner Tree Problem in a weighted graph. We show that through this approach 
we can achieve better precision, recall and speed compared to state-of-the-art 
approaches. We provide a comprehensive set of experiments supporting our 
findings.
\end{abstract}

@@

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
$ \mathcal{C}_m$ corresponds to classes in the ontology 
whereas $\mathcal{D}_m$ corresponds to data 
properties. 
Edges in the semantic model correspond to properties in the ontology, as 
shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
The semantic model may have several instances of the same ontology class or 
object property.

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{scope}
	\node[class] (pe) at (3,0)  {\small Person};
	\node[class] (co) at (6,0) {\small Org.};
	\node[class] (ci) at (1,0) {\small City};
	\node[class] (st) at (-1,0) {\small State};

	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person.name};
	\node[data] (peb) at (4.3,-0.7) {\scriptsize Person.birthDate};
	\node[data] (cin) at (1,-0.7) {\scriptsize City.name};
	\node[data] (stn) at (-1,-0.7) {\scriptsize State.name};
	\node[data] (con) at (6,-0.7) {\scriptsize Org.name};

@@

	\path[draw,hasaA,->] (st) -- (stn);
\end{scope}
\begin{scope}[yshift=-40]
	\node[class] (pl) at (-1,0)  {\small City};
	\node[class] (pe) at (3,0)  {\small Person};
	\node[class] (co) at (1,0) {\small Org.};
	\node[class] (ev) at (6,0) {\small Event};

	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person.name};
	\node[data] (evs) at (4.2,-0.7) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-0.7) {\scriptsize Event.endDate};
	\node[data] (con) at (1,-0.7) {\scriptsize Org.name};
	\node[data] (pln) at (-1,-0.7) {\scriptsize City.name};

@@

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes characteristics of the attribute such as a number 
of whitespaces and other special characters, statistics of values in the column 
(e.g, mean/max/min string length and numeric statistics) and more. A full 
list can be found in appendix \ddg{Apendix!}
One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
Shannon's entropy (or information entropy~\cite{Manning:Introduction}) of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary of all possible characters.
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

Note that we keep all the matches, regardless of the confidence of the match. 
This is an important difference between our system and other approaches 
\cite{taheriyan2016learning} that 
remove some of the matches based on heuristics in order to simplify the task of 
finding the semantic model. \ddg{is this last paragraph true?}

@@

	\node[class] (pe1) at (3,0)  {\small Person1};
	\node[class] (co1) at (6,0) {\small Org.1};
	\node[class] (ci1) at (1,0) {\small City1};
	\node[class] (st1) at (-1,0) {\small State};

	\node[data] (pen) at (2.3,0.7) {\scriptsize Person1.name};
	\node[data] (peb) at (4.2,0.7) {\scriptsize Person1.birthDate};
	\node[data] (cin) at (0.7,0.7) {\scriptsize City1.name};
	\node[data] (stn) at (-1,0.7) {\scriptsize State.name};
	\node[data] (con) at (6,0.7) {\scriptsize Org1.name};

@@

	\node[class] (pl2) at (-1,0+\ysh)  {\small City2};
	\node[class] (pe2) at (3,0+\ysh)  {\small Person2};
	\node[class] (co2) at (1,0+\ysh) {\small Org.2};
	\node[class] (ev2) at (6,0+\ysh) {\small Event};

	\node[data] (pen) at (2.3,-0.7+\ysh) {\scriptsize Person2.name};
	\node[data] (evs) at (4.2,-0.7+\ysh) {\scriptsize Event.startDate};
	\node[data] (eve) at (6,-0.7+\ysh) {\scriptsize Event.endDate};
	\node[data] (con) at (0.7,-0.7+\ysh) {\scriptsize Org2.name};
	\node[data] (pln) at (-1,-0.7+\ysh) {\scriptsize City2.name};

@@

	\node[class,orange,fill=orange!30!white,text=black] (PL) at (3,\ysh/2)  
	{\small 
	Place};

@@

\npr{reformulate for typed directed multigraphs and example based on Fig3}
In our context, patterns are typed directed graphs.
We mine these patterns from the set of semantic models in the training set $S_T$.
This is known as Transactional Frequent Graph Pattern Mining, which generalizes 
the subgraph isomorphism problem, known to be NP-complete.
The frequency of a pattern is an anti-monotonous measure, meaning that bigger 
patterns will have lower supports than their subgraphs. \ddg{Define support}
We solve this pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.  
We obtain patterns of size up to 6 in under 4 minutes for the biggest instances 
in our evaluation framework. 
\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
cite my work on how databases perform for graph pattern matching. Should it be 
better in related work?}

@@

\begin{figure}[ht]
\centering
\begin{tikzpicture}
	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{Class 
	Nodes of Alignment Graph}};

	\node[data] (stn1) at (-3.9,-0.9) {\scriptsize S.n};
	\node[data] (cin1) at (-3.1,-0.9) {\scriptsize C1.n};
	\node[data] (pen1) at (-2.3,-0.9) {\scriptsize P1.n};
	\node[data] (peb1) at (-1.5,-0.9) {\scriptsize P1.b};
	\node[data] (con1) at (-0.7,-0.9) {\scriptsize O1.n};

@@

	\node[data] (cin2) at (0.7,-1+\ysh) {\scriptsize C2.n};
	\node[data] (con2) at (1.5,-1+\ysh) {\scriptsize O2.n};
	\node[data] (pen2) at (2.3,-1+\ysh) {\scriptsize P2.n};
	\node[data] (evs2) at (3.1,-1+\ysh) {\scriptsize E.s};
	\node[data] (eve2) at (3.9,-1+\ysh) {\scriptsize E.e};

@@

Note that, although the alignment graph is directed, the semantic models are 
not necessarily rooted directed trees (e.g. Fig. \ref{FIG:sem}), therefore the 
direction of the edges is ignored for the STP model (and are all treated as 
undirected edges).

@@

It is therefore natural to model this a STP with side constraints, since the 
two first requirements imply that $T^\star$ is a Steiner Tree of the 
integration graph. By designing the weighting function $w_\mathcal{I}$ through 
ML techniques, as shown in Section \ref{SEC:ML}, 
our expectation is that the minimum weight Steiner Tree is a valid semantic 
model for the new source.

@@

\subsection{Unmatched Attributes}
It is common that the data sources to be integrated will have columns that 
simply cannot be matched to the ontology.
This can happen when a column of a source table contains some information that 
is uninteresting to the user, or because the ontology has not been properly 
designed. 
Examples of these situations can be found in domain specific data 
\cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
In current systems, these columns are removed in a process that requires 
extra time and effort as this is typically done manually in the real world.

@@

If an attribute $a$ is matched to $unk_a$, then $unk_a$ will be linked to Class 
node \emph{unknown}. 
The rest of the attributes can then be matched normally 
and build  a semantic model as usual. 
Then, to maintain connectedness of the 
Steiner tree, the \emph{unknown} node and one of the other selected Class nodes 
will 
both be connected to the \emph{root} node. 
Note that if all attributes find a 
match, then both the \emph{unknown} and \emph{root} nodes won't be selected in 
the Steiner tree and the normal behavior will take place.
\ddg{Explain the weights of the edges introduced by the unknown nodes}

@@

\ignore{We have developed a new approach for semantic labeling which can 
efficiently handle the \emph{unknown} class.}
\ignore{We demonstrate its efficiency by comparing against the state-of-the-art 
approach DSL~\cite{Pham:semantic}. } %Repeat from above
Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
DSL uses heuristic measures to capture the similarity of attributes within the same class.
It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
Our intuition as to why our approach performs better is that we have 
incorporated features which are derived directly from attribute values and are 
not based on the notion of similarity.
\npr{Good enough explanation?}

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.517753313989873)(2,0.488688737671076)(3,0.51551313872799)(4,0.495118819099343)(5,0.527778910368045)(6,0.532176796157059)(7,0.566662366701066)(8,0.637110556563823)(9,0.685799234290614)(10,0.538089511412941)(11,0.621051710776405)(12,0.599367875333495)(13,0.670421793119162)(14,0.583598347357422)(15,0.623587223886899)(16,0.645277499838855)(17,0.653525664651826)(18,0.665572696108086)(19,0.670283086011174)(20,0.663804745401859)(21,0.633242908391853)(22,0.66099516031458)(23,0.644625119528521)(24,0.72069799334011)(25,0.737468671679198)(26,0.715572819263667)(27,0.727291592547725)(28,0.752558983666062)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.551714513556619)(2,0.682453503286837)(3,0.567702774084261)(4,0.646748619299324)(5,0.65492113250734)(6,0.701065228379203)(7,0.684439263401395)(8,0.700511175298951)(9,0.681034059961129)(10,0.685637253116215)(11,0.699316636125265)(12,0.697036509934383)(13,0.693463987436823)(14,0.704225209488367)(15,0.732978923190269)(16,0.724305489322319)(17,0.699459026247245)(18,0.716210056654951)(19,0.698987880687053)(20,0.733337516584389)(21,0.751908839952318)(22,0.75007040599401)(23,0.750592804644915)(24,0.814515445676703)(25,0.810987671748541)(26,0.817791638186375)(27,0.826003784931597)(28,0.809805364617137)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.598323207198336)(2,0.656420469232034)(3,0.551668227640311)(4,0.620327113896406)(5,0.623771074555817)(6,0.652894375155994)(7,0.625071981901494)(8,0.623287932111462)(9,0.601893257814311)(10,0.601192717220153)(11,0.602088073148115)(12,0.581718160067067)(13,0.570577347465439)(14,0.572274187082211)(15,0.581600752329829)(16,0.565774690293304)(17,0.5550594629542)(18,0.565097183518236)(19,0.524149694006153)(20,0.511449953555217)(21,0.576679655627024)(22,0.571388650336019)(23,0.546588180559473)(24,0.608169608169608)(25,0.608169608169608)(26,0.633066933066933)(27,0.634654234654234)(28,0.628305028305028)
};

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.300191975130116)(2,0.387168789342702)(3,0.418780803201093)(4,0.414852632606256)(5,0.449767567691694)(6,0.454560596014134)(7,0.472473240503931)(8,0.552403403170667)(9,0.618322253509807)(10,0.45708434156857)(11,0.540246526073466)(12,0.523083348403042)(13,0.603209776078489)(14,0.509054454749254)(15,0.54874878365927)(16,0.577977828772285)(17,0.583053944903167)(18,0.591126557438254)(19,0.592414794781259)(20,0.591100946357877)(21,0.575601120513223)(22,0.587190134384184)(23,0.575949431206362)(24,0.655469912102772)(25,0.649409306042166)(26,0.64025693035835)(27,0.652378142479562)(28,0.666045239412379)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.517923133776792)(2,0.667141218952813)(3,0.56262382276875)(4,0.646790367442541)(5,0.651735815098987)(6,0.706388551614468)(7,0.698383379116542)(8,0.714984169630376)(9,0.700346244485205)(10,0.704664218197892)(11,0.717929077647748)(12,0.711690361988742)(13,0.707592621296799)(14,0.725417933239758)(15,0.760334088253952)(16,0.741766948274724)(17,0.726258869970838)(18,0.748428390280994)(19,0.723282293295816)(20,0.746991608671798)(21,0.769430045325921)(22,0.751719414109543)(23,0.756837646239269)(24,0.816669125330383)(25,0.816669125330383)(26,0.821841539123487)(27,0.824453869322024)(28,0.810608519269777)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.592810513524547)(2,0.704036744254136)(3,0.580300590445518)(4,0.665729761381935)(5,0.671789291034815)(6,0.721540066765983)(7,0.718258458411911)(8,0.728686409419572)(9,0.71549775963672)(10,0.719667189083217)(11,0.729479363111076)(12,0.713288181617252)(13,0.723866470903981)(14,0.739158277862456)(15,0.764121967041831)(16,0.755829992510182)(17,0.746486501253236)(18,0.758703555728573)(19,0.723655728717502)(20,0.729409784115667)(21,0.774654705722995)(22,0.768167419063295)(23,0.754561938768098)(24,0.828459715477971)(25,0.828459715477971)(26,0.838717192206036)(27,0.841329522404573)(28,0.833544778412933)
};
		 %\legend{karma,serene,serene-pats}

@@

The majority of approaches to solve the \relonto{} mapping problem are based on 
heuristic rules and alignment of constraints specified within relational 
schemata and ontologies.
A very comprehensive overview and comparison of existing mapping generation 
tools based on this approach is given by~\citeasnoun{Pinkel:rodi}
and~\citeasnoun{Spanos:semweb}.
As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
Further, the default ontology is enriched by using explicit and implicit schema constraints.
Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
The main advantage of these systems is the ability to run in a fully automatic setting.
Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
This opens an interesting direction for further research to develop an automatic system.

@@

\section{Conclusion}
In this paper we have introduced a new approach, \serene{} (and its extension 
that uses frequent graph patterns, \serenepats{}) to solve the problem of 
relational-to-ontology schema mapping.
Our experiments demonstrate that 
\serene{} generates on average more consistent semantic models in terms of 
precision and recall compared to the state-of-the-art approach \karma{}.
\serenepats{} produces, on average, better semantic models in terms of 
recall, and it's precision can be enhanced by adding a scaling factor for 
pattern costs.

@@

>>>>

%  \pdfinfo{
%/Title (2018 Formatting Instructions for Authors Using LaTeX)
%/Author (AAAI Press Staff)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{}
\maketitle
\begin{abstract}
The problem of integrating heterogeneous data sources in an ontology is of high 
relevance in the database field. Several techniques exist to approach this 
problem. Nonetheless, side constraints on the data integration cannot be easily 
integrated with these tools and thus the results may be inconsistent. We 
present a new approach that combines Machine Learning and 
Constraint Programming techniques, by modeling the data integration problem as 
a Steiner Tree Problem in a weighted graph. We show that through this approach 
we can achieve better precision, recall and speed compared to state-of-the-art 
approaches. We provide a comprehensive set of experiments supporting our 
findings.
\end{abstract}

@@

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
$ \mathcal{C}_m$ corresponds to classes in the ontology 
whereas $\mathcal{D}_m$ corresponds to data 
properties. 
Edges in the semantic model correspond to properties in the ontology, as 
shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
The semantic model may have several instances of the same ontology class, that is why class nodes are enumerated.

\begin{figure}[ht]
\centering
\begin{tikzpicture}
\begin{scope}
	\node[class] (pe) at (3,0)  {\small Person1};
	\node[class] (co) at (6,0) {\small Org.1};
	\node[class] (ci) at (1,0) {\small City1};
	\node[class] (st) at (-1,0) {\small State1};

	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person1.name};
	\node[data] (peb) at (4.3,-0.7) {\scriptsize Person1.birthDate};
	\node[data] (cin) at (1,-0.7) {\scriptsize City1.name};
	\node[data] (stn) at (-1,-0.7) {\scriptsize State1.name};
	\node[data] (con) at (6,-0.7) {\scriptsize Org1.name};

@@

	\path[draw,hasaA,->] (st) -- (stn);
\end{scope}
\begin{scope}[yshift=-40]
	\node[class] (pl) at (-1,0)  {\small City2};
	\node[class] (pe) at (3,0)  {\small Person2};
	\node[class] (co) at (1,0) {\small Org.2};
	\node[class] (ev) at (6,0) {\small Event1};

	\node[data] (pen) at (2.5,-0.7) {\scriptsize Person2.name};
	\node[data] (evs) at (4.2,-0.7) {\scriptsize Event1.startDate};
	\node[data] (eve) at (6,-0.7) {\scriptsize Event1.endDate};
	\node[data] (con) at (1,-0.7) {\scriptsize Org2.name};
	\node[data] (pln) at (-1,-0.7) {\scriptsize City2.name};

@@

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector, among others, includes characteristics
such as a number 
of whitespaces and other special characters, statistics of 
values in the column 
(e.g, mean/max/min string length and numeric statistics), etc. 
A full list can be found in appendix \ddg{Apendix!}
\npr{If I remove entropy descr, we are perfectly within page limit}
%\ignore{
One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
Shannon's entropy (or information entropy~\cite{Manning:Introduction}) of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary of all possible characters.
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
%}
We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

Note that we keep all the matches, regardless of the confidence of the match. 
This is an important difference between our system and other approaches 
\cite{taheriyan2016learning} that 
remove some of the matches based on heuristics in order to simplify the task of 
finding the semantic model. 
%\ddg{is this last paragraph true?} \npr{yes}

@@

	\node[class] (pe1) at (3,0)  {\small Person1};
	\node[class] (co1) at (6,0) {\small Org.1};
	\node[class] (ci1) at (1,0) {\small City1};
	\node[class] (st1) at (-1,0) {\small State1};

	\node[data] (pen) at (2.3,0.7) {\scriptsize Person1.name};
	\node[data] (peb) at (4.2,0.7) {\scriptsize Person1.birthDate};
	\node[data] (cin) at (0.7,0.7) {\scriptsize City1.name};
	\node[data] (stn) at (-1,0.7) {\scriptsize State1.name};
	\node[data] (con) at (6,0.7) {\scriptsize Org1.name};

@@

	\node[class] (pl2) at (-1,0+\ysh)  {\small City2};
	\node[class] (pe2) at (3,0+\ysh)  {\small Person2};
	\node[class] (co2) at (1,0+\ysh) {\small Org.2};
	\node[class] (ev2) at (6,0+\ysh) {\small Event1};

	\node[data] (pen) at (2.3,-0.7+\ysh) {\scriptsize Person2.name};
	\node[data] (evs) at (4.2,-0.7+\ysh) {\scriptsize Event1.startDate};
	\node[data] (eve) at (6,-0.7+\ysh) {\scriptsize Event1.endDate};
	\node[data] (con) at (0.7,-0.7+\ysh) {\scriptsize Org2.name};
	\node[data] (pln) at (-1,-0.7+\ysh) {\scriptsize City2.name};

@@

	\node[class,orange,fill=orange!30!white,text=black] (PL) at (3,\ysh/2)  
	{\small 
	Place1};

@@

%\npr{reformulate for typed directed multigraphs and example based on Fig3}
In our context, patterns are typed directed graphs.
We mine these patterns from the set of semantic models in the training set $S_T$.
This is known as Transactional Frequent Graph Pattern Mining, which includes
the subgraph isomorphism problem, known to be NP-complete.
The frequency of a pattern is the number of semantic models which contain at least one subgraph isomorphic to the pattern
The \emph{support} of the pattern is calculated as its frequency relative to the number of semantic models.
This is an anti-monotonous measure, meaning that bigger 
patterns will have lower supports than their subgraphs.
% \ddg{Define support}
We solve the pattern mining task with the tool DIMSpan \cite{petermann2017dimspan} which adapts gSpan~\cite{yan2002gspan} pruning techniques to the typed graphs and uses Apache Flink for scalability.  
We obtain patterns of size up to 6 in under 4 minutes for the biggest instances 
in our evaluation framework.
Hence, this pattern mining procedure is a highly 
scalable approach compared to the technique based on SPARQL queries 
from~\cite{Taheriyan:Leveraging}.
\npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe 
cite my work on how databases perform for graph pattern matching. Should it be 
better in related work?}

@@

\begin{figure}[ht]
\centering
\begin{tikzpicture}
	\node[class, rectangle, rounded corners] (CLASS) at (0,0) { \small{ 
	Nodes of Alignment Graph}};

	\node[data] (stn1) at (-3.9,-0.9) {\scriptsize S1.n};
	\node[data] (cin1) at (-3.1,-0.9) {\scriptsize C1.n};
	\node[data] (pen1) at (-2.3,-0.9) {\scriptsize P1.n};
	\node[data] (peb1) at (-1.5,-0.9) {\scriptsize P1.b};
	\node[data] (con1) at (-0.7,-0.9) {\scriptsize O1.n};

@@

	\node[data] (cin2) at (0.7,-1+\ysh) {\scriptsize C2.n};
	\node[data] (con2) at (1.5,-1+\ysh) {\scriptsize O2.n};
	\node[data] (pen2) at (2.3,-1+\ysh) {\scriptsize P2.n};
	\node[data] (evs2) at (3.1,-1+\ysh) {\scriptsize E1.s};
	\node[data] (eve2) at (3.9,-1+\ysh) {\scriptsize E1.e};

@@

Note that, although the alignment graph is directed, the semantic models are 
not necessarily rooted directed trees (e.g. Fig. \ref{FIG:sem}), therefore the 
direction of the edges is ignored for the STP model (and are all treated as 
undirected edges). 
\npr{This is not true: semantic models are directed. can we soften the statement here? direction of links can change semantics}

@@

It is therefore natural to model this problem as a STP with side constraints, since the 
two first requirements imply that $T^\star$ is a Steiner Tree of the 
integration graph. By designing the weighting function $w_\mathcal{I}$ through 
ML techniques, as shown in Section \ref{SEC:ML}, 
our expectation is that the minimum weight Steiner Tree is a valid semantic 
model for the new source.

@@

\subsection{Unmatched Attributes}
It is common that the data sources to be integrated will have columns that 
simply cannot be matched to the ontology.
This can happen when a column of a source table contains some information that 
is uninteresting to the user, or because the ontology has not been properly 
designed. 
Examples of these situations can be found in domain specific data 
\cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
In current systems, these columns are removed in a pre-processing step as a manual effort.

@@

If an attribute $a$ is matched to $unk_a$, then $unk_a$ will be linked to Class 
node \emph{unknown}. 
The rest of the attributes can then be matched normally 
and build  a semantic model as usual. 
To maintain connectedness of the 
Steiner tree, the \emph{unknown} node and one of the other selected Class nodes 
will 
both be connected to the \emph{root} node. 
Note that if all attributes find a 
match, then both the \emph{unknown} and \emph{root} nodes will not be selected in 
the Steiner tree and the normal behavior will take place.
The weights of the edges between these special nodes are
assigned the same way as for the rest of the edges.
%\ddg{Explain the weights of the edges introduced by the unknown nodes}

@@

\ignore{We have developed a new approach for semantic labeling which can 
efficiently handle the \emph{unknown} class.}
\ignore{We demonstrate its efficiency by comparing against the state-of-the-art 
approach DSL~\cite{Pham:semantic}. } %Repeat from above
Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
DSL uses heuristic measures to capture the similarity of attributes within the same class.
It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
Our intuition as to why our approach performs better is that we have 
incorporated features which are derived directly from attribute values and are 
not based on the notion of similarity.
%\npr{Good enough explanation?}

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.514832366157273)(2,0.520674170412197)(3,0.521026469009226)(4,0.497426082405143)(5,0.564688628672475)(6,0.55713561774315)(7,0.535076529852905)(8,0.560010216333054)(9,0.584508074744603)(10,0.546065110600816)(11,0.572489269396419)(12,0.564125297742057)(13,0.569829859460611)(14,0.543552852090991)(15,0.549734788036156)(16,0.558412528664919)(17,0.560598355931883)(18,0.607717979536758)(19,0.599585378842078)(20,0.612366200965436)(21,0.593021913264951)(22,0.623428063505196)(23,0.584747451140003)(24,0.605908308460775)(25,0.62089087544623)(26,0.607245006682788)(27,0.616141552483661)(28,0.623256309823247)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.582318872699517)(2,0.628627876837901)(3,0.609932492636812)(4,0.610866990370165)(5,0.674948143747368)(6,0.679265687227716)(7,0.70619376828754)(8,0.715634190728361)(9,0.703653042970976)(10,0.714021677870418)(11,0.718515409501215)(12,0.72006314095146)(13,0.714534069979324)(14,0.739946209262199)(15,0.741872691279687)(16,0.759026528736177)(17,0.748648620477246)(18,0.765437399193282)(19,0.749182097087044)(20,0.764528564841459)(21,0.757553110476648)(22,0.753597067073318)(23,0.757298299109379)(24,0.778783553420146)(25,0.765628808466358)(26,0.785689475530164)(27,0.768145186235277)(28,0.783815747353212)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.58839328678273)(2,0.607758082933845)(3,0.58226798181609)(4,0.591999006493134)(5,0.636658963454311)(6,0.609378189548976)(7,0.65198352100422)(8,0.639237266085298)(9,0.646381524706678)(10,0.658451931832802)(11,0.651981340743635)(12,0.639000646239548)(13,0.638100886472842)(14,0.652718769812707)(15,0.65270159785683)(16,0.665279840041019)(17,0.663658936249597)(18,0.675430261986635)(19,0.662138443878962)(20,0.662006475337153)(21,0.664124779844034)(22,0.661879115723149)(23,0.670248656767086)(24,0.677264055645277)(25,0.676979334359473)(26,0.687880411346927)(27,0.67459653454876)(28,0.68627902145454)
};

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.367995759495435)(2,0.43314958257729)(3,0.465102732953193)(4,0.446507314880989)(5,0.506469092210478)(6,0.506789578789452)(7,0.477080991784194)(8,0.503937397649502)(9,0.534229842849261)(10,0.492507267102593)(11,0.515796460946058)(12,0.509165531142068)(13,0.516097781643373)(14,0.488160651098756)(15,0.496282029692244)(16,0.504382820425249)(17,0.503923406733149)(18,0.552759367968562)(19,0.540550359776821)(20,0.554759177609889)(21,0.53688314428863)(22,0.561628603103704)(23,0.525601546354885)(24,0.548689620179471)(25,0.559372079917562)(26,0.54849327148799)(27,0.558777769863011)(28,0.561036686567106)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.568526176536315)(2,0.612789529917517)(3,0.603758658205161)(4,0.611122761022995)(5,0.679226888229885)(6,0.689545922126768)(7,0.718173517817693)(8,0.72049339757837)(9,0.712025690044822)(10,0.719376710211083)(11,0.719738340274138)(12,0.727571790593847)(13,0.718652567615389)(14,0.742375410864123)(15,0.744789115461273)(16,0.761896901012414)(17,0.753562034501087)(18,0.768934123583718)(19,0.753381510225111)(20,0.767814904456983)(21,0.758472395730288)(22,0.753685690354242)(23,0.754906882661518)(24,0.772285894201019)(25,0.771337684854641)(26,0.782427299035871)(27,0.762524256400432)(28,0.778430045086962)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.596084829534507)(2,0.640760186457491)(3,0.62082780704382)(4,0.636003942692136)(5,0.692664734541117)(6,0.701974230777832)(7,0.728319438123534)(8,0.750185705723487)(9,0.736888107321033)(10,0.742404159647386)(11,0.743250566844835)(12,0.732378757282814)(13,0.729581368486718)(14,0.7525692913614)(15,0.751549245497265)(16,0.767850111275969)(17,0.762600014025882)(18,0.778934826315818)(19,0.764342969952451)(20,0.767198788345341)(21,0.761867162993121)(22,0.765611676236013)(23,0.768814394670878)(24,0.779481328123055)(25,0.783142085550363)(26,0.789525770002408)(27,0.774378390471089)(28,0.790117094780008)
};
		 %\legend{karma,serene,serene-pats}

@@

The majority of approaches to solve the \relonto{} mapping problem are based on 
heuristic rules and alignment of constraints specified within relational 
schemata and ontologies.
A very comprehensive overview and comparison of existing mapping generation 
tools based on this approach is given by~\citeasnoun{Pinkel:rodi}
and~\citeasnoun{Spanos:semweb}.
As examples, there are BootOX~\cite{Jimenez:Bootox}, MIRROR~\cite{Luciano:Mirror} and  ontop~\cite{Fagin:Clio}.
Crudely speaking, these tools first apply a default direct mapping specified by the W3C.
Further, the default ontology is enriched by using explicit and implicit schema constraints.
Finally, ontology alignment techniques are applied to match the default ontology to the target ontology.
The main advantage of these systems is the ability to run in a fully automatic setting.
Our approach is complementary to the approaches from this group and at its current stage is semi-automatic.
However, constraint programming offers a convenient framework to incorporate integrity constraints specified either within relational or ontological schema as additional constraints to govern the search for the solution.
This opens an interesting direction for further research.

@@

\section{Conclusion}
In this paper we have introduced a new approach, \serene{} (and its extension 
that uses frequent graph patterns, \serenepats{}) to solve the problem of 
relational-to-ontology schema mapping.
Our experiments demonstrate that 
\serene{} generates on average more consistent semantic models in terms of 
precision and recall compared to the state-of-the-art approach \karma{}.
\serenepats{} produces, on average, better semantic models in terms of 
recall, and its precision can be enhanced by adding a scaling factor for 
pattern costs.

@@

\newpage
